Stateless Model Checking with Data-Race Preemption Points

### 2016-07-16 oopsla-16/related.tex
finish related work related revisions

\revision{{\bf Restricting preemptions.}
Preemption Sealing \cite{sealing} pre\-sents a mechanism similar to the {\tt within\_function} command (\sect{\ref{sec:landslide}}) for users to manually restrict preemptions.
It demonstrates the need to consider subsets of PPs,
as well as developers' willingness to limit a test case's scope so the resulting state space may be fully verified (\sect{\ref{sec:totalverif}}).
%It justifies our assumption that expert
%programmers can customize small test cases which, when fully verified,
%provide a correctness assurance much stronger than the assurance from
%a partially-complete exploration of a huge state space.
Probabilistic Concurrency Testing (PCT) \cite{randomized-scheduler}
is a randomized algorithm that can quantify the probability of uncovering bugs.
PCT is optimized for tests with impossibly large state spaces,
while for more approachable tests,
its incompatibility with DPOR would significantly delay completion.
Future work could use ETAs to heuristically switch between DPOR and PCT}.
Finally, ICB \cite{chess-icb} is most similar to our work,
as both approaches provide a partial verification
%on some subset of interleavings
when full completion is intractable (\sect{\ref{sec:future}}).
However, ICB is limited to a fixed set of PPs,
\revision{cannot estimate remaining time to total verification,
and can incorporate data-race PPs only when statically coded in advance}.
%and to our knowledge no algorithm has been proposed to dynamically add data-race PPs during a test with ICB.

>>>>

\revision{{\bf Restricting preemptions.}
Preemption Sealing \cite{sealing} pre\-sents a mechanism similar to the {\tt within\_function} command (\sect{\ref{sec:landslide}}) for users to manually restrict preemptions.
It demonstrates the need to consider subsets of PPs,
as well as developers' willingness to limit a test case's scope so the resulting state space may be fully verified (\sect{\ref{sec:totalverif}}).
%It justifies our assumption that expert
%programmers can customize small test cases which, when fully verified,
%provide a correctness assurance much stronger than the assurance from
%a partially-complete exploration of a huge state space.
Probabilistic Concurrency Testing (PCT) \cite{randomized-scheduler}
is a randomized algorithm that can quantify the probability of uncovering bugs.
PCT \revisionx{targets} tests with impossibly large state spaces,
\revisionx{eschewing DPOR's depth-first search model to
%ensure it can
quickly sample a broad cross-section of large state spaces.
However, it proposes no alternate reduction algorithm to make up for its incompatibility with DPOR,
so is unsuitable for verification of medium-sized tests.}
%while for more approachable tests,
%its incompatibility with DPOR would significantly delay completion.
Future work could use ETAs to heuristically switch between DPOR and PCT}.
%
Finally, ICB \cite{chess-icb} is most similar to our work,
as both approaches provide a partial verification
%on some subset of interleavings
when full completion is intractable (\sect{\ref{sec:future}}).
However, ICB
%is limited to a fixed set of PPs,
\revision{cannot estimate remaining time to total verification,
and can incorporate data-race PPs only when statically coded in advance}.
\revisionx{Our results in \sect{\ref{sec:eval-sssmc}} outperform both such configurations of ICB.}
%and to our knowledge no algorithm has been proposed to dynamically add data-race PPs during a test with ICB.
